Optimal Fitting of Planar Curves to Prescribed Constraints

### 2014-01-26 idp/documentation/paper.tex
moved math macros
improved finding curves as optimization problem slide

\usepackage[utf8]{inputenc}    % enables use of utf8 characters in the input file
\usepackage[T1]{fontenc}       % enables proper output of unicode characters such that text can be copy-pasted from the pdf file
\usepackage{hyperref}          % enables pdf index, links for web addresses, intra-document links
\usepackage{a4wide}            % reduces page margins
\usepackage{parskip}           % replaces hanging paragraphs with spacing between paragraphs
\usepackage{times}             % replaces Computer Modern font with something resembling Times
\usepackage{textcomp}          % adds symbols like \textdegree
\usepackage{graphicx}          % enables including graphics
\usepackage{amsmath}           % ams math module
\usepackage{amssymb}           % ams math symbols
\usepackage{mathtools}         % fixes a few quirks with the ams packages

\input{math.tex}               % some math helper macros

@@

				In the following, we will describe how nonlinear optimization can be used for building polynomial splines based on descriptions in the language established in section \ref{section:description_language}.

			\subsubsection{Segmentation and Notation}
			\label{section:segmentation_notation}

@@

>>>>

\usepackage[utf8]{inputenc}    % enables use of utf8 characters in the input file
\usepackage[T1]{fontenc}       % enables proper output of unicode characters such that text can be copy-pasted from the pdf file
\usepackage{hyperref}          % enables pdf index, links for web addresses, intra-document links
\usepackage{a4wide}            % reduces page margins
\usepackage{parskip}           % replaces hanging paragraphs with spacing between paragraphs
\usepackage{times}             % replaces Computer Modern font with something resembling Times
\usepackage{graphicx}          % enables including graphics
\usepackage{amsmath}           % ams math module
\usepackage{amssymb}           % ams math symbols
\usepackage{mathtools}         % fixes a few quirks with the ams packages

\input{../common/math.tex}     % some math helper macros

@@

				In the following, we will describe how nonlinear optimization can be used for finding polynomial splines based on descriptions in the language established in section \ref{section:description_language}.

			% TODO: consider structuring and naming this section similarly to the slides
			\subsubsection{Segmentation and Notation}
			\label{section:segmentation_notation}

				%\begin{equation*}
				%	\apply{\phi_i}{t} = \sum_j a_{i,j} \cdot t^j
				%\end{equation*}

@@

			% idea seems good, optimization issues get in the way
			% maybe move this to conclusion
